Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Add TODOs to Data Analysis

% TODO: Describe general synthesis process, focusing on input and output
% TODO: List all criteria with details
% TODO: Try to express criteria as metrics
% TODO: Put special focus on those Natural Language Processing
% TODO: Maybe mention, that our synthesis contains actions that may have belonged into extraction, but we found the terms more fitting to our implementation

@@

Data analysis would be concerned with any sort of statistical quality
analysis of the data. More specifically, the subsection on data
analysis is concerned with issues like the following:

\begin{itemize}

\item Simple statistics like median of metrics.

\item Analysis of regression or correlation or distribution.

\item Analysis of accuracy such as precision and recall.

\end{itemize}

It should be noted that the methodology section describes the `how'
(and to some extent the`why'), but it does not yet report the various
results; see the following section. For instance, the methodology may
explain why it is using a certain metric and define it and announce
that the median for the metric is going to be determined, as it would
provide a certain insight, but the actual tables or charts for the
metric and the interpretation of the findings would be deferred to the
results section.

>>>>

% TODO: Describe general synthesis process, focusing on input and output
% TODO: List all criteria with details
% TODO: Try to express criteria as metrics. I guess we count how many of an author's commits meet each criterion, and that count is our metric.
% TODO: Put special focus on those Natural Language Processing
% TODO: Maybe mention, that our synthesis contains actions that may have belonged into extraction, but we found the terms more fitting to our implementation

@@

% Data analysis would be concerned with any sort of statistical quality
% analysis of the data. More specifically, the subsection on data
% analysis is concerned with issues like the following:
%
% \begin{itemize}
%
% \item Simple statistics like median of metrics.
%
% \item Analysis of regression or correlation or distribution.
%
% \item Analysis of accuracy such as precision and recall.
%
% \end{itemize}
%
% It should be noted that the methodology section describes the `how'
% (and to some extent the`why'), but it does not yet report the various
% results; see the following section. For instance, the methodology may
% explain why it is using a certain metric and define it and announce
% that the median for the metric is going to be determined, as it would
% provide a certain insight, but the actual tables or charts for the
% metric and the interpretation of the findings would be deferred to the
% results section.

% TODO: Decide on analysis tools
% * Weka
% * Some Boxplots including averages for all metrics
% TODO: Introduce the analysis tools we used
